---
title: "LMM Models"
author: "Benjamin Wade"
format: html
editor: visual
---

# Notes

## Helper functions

```{r}
# log-mod transformation 
log_mod_transform <- function(x){
  lmt <- sign(x) * log(abs(x) + 1)
  return(lmt)
}

# reverse log-mod transformation
log_inv_transform <- function(x){
  inv_lmt <- sign(x) * (exp(abs(x)) - 1)
  return(inv_lmt)
}

# power calculation
power_estimate <- function(fit, fixed_effect, es, nsim=50){
  fixef(fit)[fixed_effect] <- es
  set.seed(123)
  res <- powerSim(fit, test = fixed(fixed_effect, "t"), nsim = nsim)
  print(res)
}
```

## Load and format data

```{r}
#| include: false
require(lme4)
require(lmerTest)
require(sjPlot)
require(sjmisc)
require(effects)
require(sjstats)
require(ggplot2)
require(ggrepel)
require(ggpubr)
require(ggeffects)
require(tidyverse)
require(dplyr)
require(tableone)
require(knitr)
require(lcmm)
require(reshape2)
require(MuMIn)
require(mediation)
require(tableone)
require(performance)
require(gtsummary)
require(emmeans)
require(simr)

emm_options(pbkrtest.limit = 6000)
emm_options(rg.limit = 900000)
```

```{r}
per_protocol_cohort <- FALSE
days_contrast <- c(-10, 0, 1, 5, 10, 12, 15, 30, 45)
est_power <- FALSE
save_table <- TRUE
path_figures <- NULL
path_tables <- '/path/to/tables/'
```

```{r}
# load formatted data
load('/path/to.Rdata')

# make time_first_infusion_to_phq numeric
ember_data$time_first_infusion_to_phq <- as.numeric(ember_data$time_first_infusion_to_phq)

# Center time variable: No scaling
ember_data$time_first_infusion_to_phq_centered <- scale(ember_data$time_first_infusion_to_phq, center = TRUE, scale = FALSE)

# Add log-modulus transformation of time to handle negative cases
ember_data$time_first_infusion_to_phq_log_mod <- log_mod_transform(as.numeric(ember_data$time_first_infusion_to_phq))

# center and scale age
ember_data$age_years_centered_scaled <- scale(ember_data$age_years, center = TRUE, scale = TRUE)

# add baseline symptoms and save persistent version
ember_data_saved <- ember_data %>%
  group_by(client_id) %>%
  arrange(date_submitted_phq, .by_group = TRUE) %>%
  mutate(baseline_phq = dplyr::first(phq_tot), 
         end_phq = dplyr::last(phq_tot),
         min_phq = min(phq_tot), 
         days_first_infusion_to_final_phq = last(date_submitted_phq) - first_infusion_completed,
         days_first_phq_to_final_phq = last(date_submitted_phq) - first(date_submitted_phq),
         baseline_si_any = ifelse(dplyr::first(phq9) > 0, 1, 0),
         baseline_si_mod_sev = ifelse(dplyr::first(phq9) > 1, 1, 0),
         end_si_any = ifelse(dplyr::last(phq9) > 0, 1, 0),
         end_si_mod_sev = ifelse(dplyr::last(phq9) > 1, 1, 0),
         baseline_si_score = first(phq9),
         end_si_score = last(phq9),
         min_si_score = min(phq9))

# sex as factor
ember_data_saved$sex_assigned_at_birth <- as.factor(ember_data_saved$sex_assigned_at_birth)

# reset medication names to old codes
ember_data_saved <- ember_data_saved %>%
  rename("antidepressant_load"="antidepressant",
         "antipsychotic_load"="antipsychotic",
         "stimulant_load"="stimulant",
         "benzodiazepine_load"="benzodiazepine",
         "mood_stabilizer_load"="mood_stabilizer",
         "non_benzodiazepine_anxiolytic_sedative_load"="nbas",
         "other_psychotropic_medication_load"="other_psychotropic_medication")

# # drop zero-variance variable(s)
# ember_data_saved <- ember_data_saved %>%
#   dplyr::select(-non_benzodiazepine_anxiolytic_sedative_load)

# set NA medications to zero
ember_data_saved$antidepressant_load[which(is.na(ember_data_saved$antidepressant_load))] <- 0
ember_data_saved$antipsychotic_load[which(is.na(ember_data_saved$antipsychotic_load))] <- 0
ember_data_saved$benzodiazepine_load[which(is.na(ember_data_saved$benzodiazepine_load))] <- 0
ember_data_saved$non_benzodiazepine_anxiolytic_sedative_load[which(is.na(ember_data_saved$non_benzodiazepine_anxiolytic_sedative_load))] <- 0
ember_data_saved$mood_stabilizer_load[which(is.na(ember_data_saved$mood_stabilizer_load))] <- 0
ember_data_saved$other_psychotropic_medication_load[which(is.na(ember_data_saved$other_psychotropic_medication_load))] <- 0
ember_data_saved$stimulant_load[which(is.na(ember_data_saved$stimulant_load))] <- 0

# binarize medications: 0 = 0; 1 = > 0
ember_data_saved <- ember_data_saved %>%
  mutate(antidepressant_load = factor(ifelse(antidepressant_load > 0, 1, 0))) %>%
  mutate(antipsychotic_load = factor(ifelse(antipsychotic_load > 0, 1, 0))) %>%
  mutate(benzodiazepine_load = factor(ifelse(benzodiazepine_load > 0, 1, 0))) %>%
  mutate(non_benzodiazepine_anxiolytic_sedative_load = factor(ifelse(non_benzodiazepine_anxiolytic_sedative_load > 0, 1, 0))) %>%
  mutate(mood_stabilizer_load = factor(ifelse(mood_stabilizer_load > 0, 1, 0))) %>%
  mutate(other_psychotropic_medication_load = factor(ifelse(other_psychotropic_medication_load > 0, 1, 0))) %>%
  mutate(stimulant_load = factor(ifelse(stimulant_load > 0, 1, 0))) %>%
  as.data.frame()

# set reference level for medications
ember_data_saved$antidepressant_load <- relevel(ember_data_saved$antidepressant_load, ref = "0")
ember_data_saved$antipsychotic_load <- relevel(ember_data_saved$antipsychotic_load, ref = "0")
ember_data_saved$benzodiazepine_load <- relevel(ember_data_saved$benzodiazepine_load, ref = "0")
ember_data_saved$non_benzodiazepine_anxiolytic_sedative_load <- relevel(ember_data_saved$non_benzodiazepine_anxiolytic_sedative_load, ref = "0")
ember_data_saved$mood_stabilizer_load <- relevel(ember_data_saved$mood_stabilizer_load, ref = "0")
ember_data_saved$stimulant_load <- relevel(ember_data_saved$stimulant_load, ref = "0")
ember_data_saved$other_psychotropic_medication_load <- relevel(ember_data_saved$other_psychotropic_medication_load, ref = "0")

# set reference level for age cagtegory
ember_data_saved$age_bin <- relevel(ember_data_saved$age_bin, ref = 'adult')
```

## Apply I/E Criteria

```{r}
# per protocol only
if(per_protocol_cohort){
  print("Per Protocol Cohort")
  ember_data_saved <- ember_data_saved %>% filter(per_protocol == 1)
}else{
  print("Intention to Treat Cohort")
}

# exclude adolescents
adolecent_ids <- unique(ember_data_saved$client_id[which(ember_data_saved$age_years < 18)])
ember_data_saved <- ember_data_saved[!ember_data_saved$client_id %in% adolecent_ids, ]

ember_data_saved <- ember_data_saved %>%
  filter(age_bin != 'adolescent')
ember_data_saved$age_bin <- droplevels(ember_data_saved$age_bin)

# exclude anyone in pre-treatment or ongoing treatment phase
ember_data_saved <- ember_data_saved %>% filter(foundation_completion_status != "Pre/In Treatment")

# exclude long-term care (LTC) visits
ember_data_saved <- ember_data_saved[ember_data_saved$date_submitted_phq <= ember_data_saved$first_ltc_infusion_date | is.na(ember_data_saved$first_ltc_infusion_date), ]

# exclude outcomes with missing underlying items
missing_items <- which(is.na(ember_data_saved[, grep('phq[1-9]$', names(ember_data_saved), value = T)]), arr.ind = T)
missing_items <- missing_items[, 1]

print(sprintf("Excluding outcomes from %s observations", length(missing_items)))
print(ember_data_saved$client_id[missing_items])

ember_data_saved$phq_tot[missing_items] <- NA
```

## Patient Table

```{r}
tab <-
  ember_data_saved %>%
  mutate(primary_diagnosis = ifelse(primary_diagnosis_bipolar==1, "BD", "MDD")) %>%
  group_by(client_id) %>%
  arrange(date_submitted_phq, .by_group = TRUE) %>%
  mutate(baseline_phq = dplyr::first(phq_tot), 
         end_phq = dplyr::last(phq_tot)) %>%
  slice_min(order_by = date_submitted_phq, n = 1) %>%
  rename("sex"="sex_assigned_at_birth",
         "age"="age_years",
         "health_insurance"="do_you_have_health_insurance",
         "two_meds_five_years"="have_you_tried_more_than_two_medications_for_your_depressive_symptoms_in_the_past_five_years",
         "two_meds_lifetime"="have_you_tried_more_than_two_medications_for_your_depressive_symptoms_in_your_lifetime",
         "tried_tms"="have_you_tried_transcranial_magnetic_stimulation_tms",
         "tried_ect"="have_you_tried_electroconvulsive_therapy_ect",
         "tobacco"="use_tobacco_yes",
         "cannabis"="use_cannabis_yes",
         "alcohol"="drink_alcohol_yes",
         "other_substances"="use_other_recreational_substances_yes",
         "heart_disease_stroke"="heart_disease_stroke_yes",
         "high_bp"="high_blood_pressure_yes",
         "diabetes"="diabetes_yes",
         "cancer"="cancer_specify_type_yes",
         "bipolar"="primary_diagnosis_bipolar",
         "anxiety"="comorbid_anxiety",
         "ocd"="comorbid_ocd",
         "ptsd"="comorbid_ptsd",
         "sud"="comorbid_sud") %>%
  ungroup() %>%
  distinct(client_id, .keep_all = TRUE) %>%
  tbl_summary(include = c(age, age_bin, sex, baseline_phq, end_phq, min_phq, baseline_si_any, end_si_any, baseline_si_mod_sev, end_si_mod_sev, baseline_si_score, end_si_score, min_si_score, days_first_infusion_to_final_phq, days_first_phq_to_final_phq, foundation_completion_status,
                          health_insurance,two_meds_five_years,two_meds_lifetime, tried_tms,
                          tried_ect, tobacco, cannabis, alcohol, other_substances,
                          heart_disease_stroke, high_bp, diabetes, cancer, anxiety,
                          ocd, ptsd, sud, antidepressant_load, antipsychotic_load, benzodiazepine_load, non_benzodiazepine_anxiolytic_sedative_load,
                          mood_stabilizer_load,
                          stimulant_load, other_psychotropic_medication_load),
              by=primary_diagnosis,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
  add_overall() %>%
  add_p() %>%
  separate_p_footnotes() %>%
  modify_header(label = "**Variable**") %>%
  add_variable_group_header(
    header = "Demographics",
    variables = c("age", "age_bin", "sex")) %>%
  add_variable_group_header(
    header = "Symptoms",
    variables = c("baseline_phq", "end_phq", "min_phq", "baseline_si_any", "end_si_any", "baseline_si_mod_sev", "end_si_mod_sev", "baseline_si_score", "end_si_score", "min_si_score", "days_first_infusion_to_final_phq", "days_first_phq_to_final_phq")) %>%
  add_variable_group_header(
    header = "Comorbid Psychiatric",
    variables = c("anxiety", "ocd", "ptsd", "sud")) %>%
  add_variable_group_header(
    header = "General Health",
    variables = c("heart_disease_stroke", "high_bp",
                  "diabetes", "cancer", "tobacco", 
                  "cannabis", "alcohol")) %>%
  add_variable_group_header(
    header = "Medications",
    variables = ends_with("_load")) %>%
  bold_labels()

tab

if(save_table){
  gt_table <- as_gt(tab) 
  gt::gtsave(gt_table, filename = paste0(path_tables, "ember_table_1.docx")) 
}
```

## Time Point Frequency

```{r}
hist(as.numeric(ember_data_saved$time_first_infusion_to_phq), 
     col = 'steelblue', 
     xlab = "Days", 
     main = "Days First Foundational Infusion to PHQ")

hist(as.numeric(ember_data_saved$time_last_foundational_infusion_to_phq),
      col = 'steelblue', 
     xlab = "Days", 
     main = "Days Last Foundational Infusion to PHQ")
```

## Plot functions

```{r}
plot_trajectories_by_group <- function(fit, diagnosis, days_list, diagnosis_2 = NULL, num_levels = NULL){
  
  if(!is.null(num_levels)){
    col_palette <- c("steelblue2", "firebrick3", "chartreuse")
  }else{
    col_palette <- c("steelblue2", "firebrick3")
  }
  
  if(!is.null(diagnosis_2)){
    form <- as.formula(paste(diagnosis, "~ time_first_infusion_to_phq_log_mod | ", diagnosis_2))
  }else{
    form <- as.formula(paste(diagnosis, "~ time_first_infusion_to_phq_log_mod"))  
  }
  
  plt_data <- emmip(fit, form,
                    CI = TRUE,
                    type = "response",
                    at = list(time_first_infusion_to_phq_log_mod = c(log_mod_transform(days_list)))) + 
    labs(x = "Days from first infusion to PHQ-9", y = "Predicted PHQ-9 score") +
    scale_color_manual(values = col_palette) + 
    theme_bw()
  
  plt_data$data <- plt_data$data %>%
    as.data.frame() %>%
    mutate(xvar = log_inv_transform(xvar))
  
  plt_data
}
```

## Effect size for estimated marginal means function

```{r}
tabulate_effect_size <- function(fit, diagnosis, days_list){
  
  form <- as.formula(paste0("revpairwise ~ ", diagnosis, "| time_first_infusion_to_phq_log_mod")) 
  
  emm <- emmeans(fit, 
             specs = form,
             at = list(time_first_infusion_to_phq_log_mod = log_mod_transform(days_contrast)),
             infer = TRUE,
             null = 0,
             adjust = "mvt")
  
  # transform grid to time in days: inverse log transform
  emm$contrasts@levels$time_first_infusion_to_phq_log_mod <- log_inv_transform(emm$contrasts@levels$time_first_infusion_to_phq_log_mod)
  emm$contrasts@grid$time_first_infusion_to_phq_log_mod <- log_inv_transform(emm$contrasts@grid$time_first_infusion_to_phq_log_mod)

  
  # Calculate Cohen's d
  sigma_value <- sigma(fit)          # Population SD
  edf_value <- df.residual(fit)      # Degrees of freedom
  cd <- eff_size(emm, sigma = sigma_value, edf = edf_value)
  
  print(cd)

}

```

## Model 1: Symptoms over time

```{r}
predictors <- c("baseline_phq", "age_years_centered_scaled",
                  "sex_assigned_at_birth", "per_protocol",
                  grep("^comorbid_|^primary_diagnosis|baseline_si_any", names(ember_data_saved), value=TRUE),
                  grep('^total', grep('load$', names(ember_data_saved), value = T), value = T, invert = T))

fixed_effects <- paste0(paste0(predictors, collapse=" + "), " + time_first_infusion_to_phq_log_mod")
  
form <- reformulate(paste(fixed_effects, "+ (1 | client_id)"), response='phq_tot')

print(form)
  
fit_log_mod <- lmer(form, data = ember_data_saved, REML = FALSE)
```

### Coefficient table

```{r}
sjPlot::tab_model(fit_log_mod, p.adjust = "fdr", show.stat = TRUE, show.df = TRUE,
                  file = paste0(path_tables, 'ember_coefficient_table_main_effects.doc'))
```

### Plot predicted symptom trajectories

```{r}
ggpredict(fit_log_mod, "time_first_infusion_to_phq_log_mod [sample=50]") %>%
  as.data.frame() %>%
  mutate(x = sign(x) * exp(abs(x)) - 1) %>% # convert log-mod-time to original scale: sign(x) * (exp(abs(x)) - 1) 
  ggplot(aes(x = x, y = predicted)) +
  geom_line(col = 'steelblue2', linewidth = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  labs(x = "Days from first infusion to PHQ-9", y = "Predicted PHQ-9 score") +
  theme_bw()
```

### Model diagnostics

```{r}
#| fig-height: 10
#| fig-width: 8
performance::check_model(fit_log_mod)

if(est_power){
 power_estimate(fit_log_mod, fixed_effect = "time_first_infusion_to_phq_log_mod", es = 0.3) 
}
```

## Model 2: Symptoms over time: categorical age

```{r}
predictors <- c("baseline_phq", "age_bin",
                  "sex_assigned_at_birth", "per_protocol",
                  grep("^comorbid_|^primary_diagnosis|baseline_si_any", names(ember_data_saved), value=TRUE),
                  grep('^total', grep('load$', names(ember_data_saved), value = T), value = T, invert = T))

fixed_effects <- paste0(paste0(predictors, collapse=" + "), " + time_first_infusion_to_phq_log_mod")
  
form <- reformulate(paste(fixed_effects, "+ (1 | client_id)"), response='phq_tot')

print(form)
  
fit_log_mod_age_bin <- lmer(form, data = ember_data_saved, REML = FALSE)
```

### Coefficient table

```{r}
sjPlot::tab_model(fit_log_mod_age_bin, p.adjust = "fdr", show.stat = TRUE, show.df = TRUE,
                  file = paste0(path_tables, 'ember_coefficient_table_main_effects.doc'))
```

## Model 3: Interactions with time

```{r}
fit_unified_log_mod_time <- 
  lmer(phq_tot ~ baseline_phq + time_first_infusion_to_phq_log_mod *   
         (sex_assigned_at_birth + age_years_centered_scaled + per_protocol + 
                                                 primary_diagnosis_bipolar + comorbid_anxiety + 
                                                 comorbid_ocd + comorbid_ptsd + comorbid_sud + 
                                                 baseline_si_any + 
                                                 antidepressant_load + antipsychotic_load + 
                                                 benzodiazepine_load + non_benzodiazepine_anxiolytic_sedative_load + 
                                                 mood_stabilizer_load + 
                                                 stimulant_load + 
                                                 other_psychotropic_medication_load) +
         (1|client_id), 
       data = ember_data_saved, 
       REML = TRUE)
```

### Coefficient table

```{r}
sjPlot::tab_model(fit_unified_log_mod_time, p.adjust = "fdr", show.stat = TRUE, show.df = TRUE,
                  file = paste0(path_tables, 'ember_coefficient_table_interaction_effects.doc'))
```

### Plot predicted symptom trajectories by primary diagnosis

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'primary_diagnosis_bipolar',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'primary_diagnosis_bipolar',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by anxiety

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'comorbid_anxiety',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'comorbid_anxiety',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by OCD

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'comorbid_ocd',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'comorbid_ocd',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by PTSD

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'comorbid_ptsd',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'comorbid_ptsd',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by SUD

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'comorbid_sud',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'comorbid_sud',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by SI

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'baseline_si_any',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'baseline_si_any',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by antidepressants

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'antidepressant_load',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'antidepressant_load',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by antipsychotics

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'antipsychotic_load',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'antipsychotic_load',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by benzodiazepines

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'benzodiazepine_load',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'benzodiazepine_load',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by benzodiazepines

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'non_benzodiazepine_anxiolytic_sedative_load',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'non_benzodiazepine_anxiolytic_sedative_load',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by mood stabilizers

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'mood_stabilizer_load',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'mood_stabilizer_load',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by stimulants

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'stimulant_load',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'stimulant_load',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by other psychotropic medications

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'other_psychotropic_medication_load',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'other_psychotropic_medication_load',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by sex

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'sex_assigned_at_birth',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'sex_assigned_at_birth',
                           days_list = days_contrast)
```

### Plot predicted symptom trajectories by per-protocol

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time,
                           diagnosis = 'per_protocol',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time, 
                           diagnosis = 'per_protocol',
                           days_list = days_contrast)
```

### Model diagnostics

```{r}
#| fig-height: 10
#| fig-width: 8
performance::check_model(fit_unified_log_mod_time)
```

## Model 4: Interactions with time: categorical age

```{r}
fit_unified_log_mod_time_age_bin <- 
  lmer(phq_tot ~ baseline_phq + time_first_infusion_to_phq_log_mod *   (sex_assigned_at_birth + age_bin + per_protocol +
                                                 primary_diagnosis_bipolar + comorbid_anxiety + 
                                                 comorbid_ocd + comorbid_ptsd + comorbid_sud + 
                                                 baseline_si_any + 
                                                 antidepressant_load + antipsychotic_load + 
                                                 benzodiazepine_load + non_benzodiazepine_anxiolytic_sedative_load + 
                                                 mood_stabilizer_load + 
                                                 stimulant_load + 
                                                 other_psychotropic_medication_load) +
         (1|client_id), 
       data = ember_data_saved, 
       REML = TRUE)
```

### Coefficient table

```{r}
sjPlot::tab_model(fit_unified_log_mod_time_age_bin, p.adjust = "fdr", show.stat = TRUE, show.df = TRUE, file = paste0(path_tables, 'ember_coefficient_table_interaction_effects_age_bins.doc'))
```

### Plot predicted symptom trajectories by age category

```{r}
plot_trajectories_by_group(fit = fit_unified_log_mod_time_age_bin,
                           diagnosis = 'age_bin',
                           days_list = days_contrast) 
```

### Report effect sizes

```{r}
tabulate_effect_size(fit = fit_unified_log_mod_time_age_bin, 
                           diagnosis = 'age_bin',
                           days_list = days_contrast)
```
