---
title: "Model Comparison"
author: "Benjamin Wade"
format: html
editor: visual
---

# Notes

## Helper functions

```{r}
# log-mod transformation 
log_mod_transform <- function(x){
  lmt <- sign(x) * log(abs(x) + 1)
  return(lmt)
}

# reverse log-mod transformation
log_inv_transform <- function(x){
  inv_lmt <- sign(x) * (exp(abs(x)) - 1)
  return(inv_lmt)
}

# power calculation
power_estimate <- function(fit, fixed_effect, es, nsim=50){
  fixef(fit)[fixed_effect] <- es
  set.seed(123)
  res <- powerSim(fit, test = fixed(fixed_effect, "t"), nsim = nsim)
  print(res)
}
```

## Load and format data

```{r}
#| include: false
require(lme4)
require(lmerTest)
require(sjPlot)
require(sjmisc)
require(effects)
require(sjstats)
require(ggplot2)
require(ggrepel)
require(ggpubr)
require(ggeffects)
require(tidyverse)
require(dplyr)
require(tableone)
require(knitr)
require(lcmm)
require(reshape2)
require(MuMIn)
require(mediation)
require(tableone)
require(performance)
require(gtsummary)
require(emmeans)
require(simr)

emm_options(pbkrtest.limit = 5000)
emm_options(rg.limit = 500000)
```

```{r}
per_protocol_cohort <- FALSE
days_contrast <- c(-10, 0, 1, 5, 10, 12, 15, 30, 45)
est_power <- FALSE
save_table <- TRUE
```

```{r}
# load formatted data
load('/path/to/data')

# make time_first_infusion_to_phq numeric
ember_data$time_first_infusion_to_phq <- as.numeric(ember_data$time_first_infusion_to_phq)

# Center time variable: No scaling
ember_data$time_first_infusion_to_phq_centered <- scale(ember_data$time_first_infusion_to_phq, center = TRUE, scale = FALSE)

# Add log-modulus transformation of time to handle negative cases
ember_data$time_first_infusion_to_phq_log_mod <- log_mod_transform(as.numeric(ember_data$time_first_infusion_to_phq))

# center and scale age
ember_data$age_years_centered_scaled <- scale(ember_data$age_years, center = TRUE, scale = TRUE)

# add baseline symptoms and save persistent version
ember_data_saved <- ember_data %>%
  group_by(client_id) %>%
  #arrange(time_point, .by_group = TRUE) %>%
  arrange(date_submitted_phq, .by_group = TRUE) %>%
  mutate(baseline_phq = dplyr::first(phq_tot), 
         end_phq = dplyr::last(phq_tot),
         min_phq = min(phq_tot),
         days_first_infusion_to_final_phq = last(date_submitted_phq) - first_infusion_completed,
         days_first_phq_to_final_phq = last(date_submitted_phq) - first(date_submitted_phq)) %>%
  mutate(baseline_si_any = ifelse(dplyr::first(phq9) > 0, 1, 0)) %>%
  mutate(baseline_si_mod_sev = ifelse(dplyr::first(phq9) > 1, 1, 0))

# sex as factor
ember_data_saved$sex_assigned_at_birth <- as.factor(ember_data_saved$sex_assigned_at_birth)

# reset medication names to old codes
ember_data_saved <- ember_data_saved %>%
  rename("antidepressant_load"="antidepressant",
         "antipsychotic_load"="antipsychotic",
         "stimulant_load"="stimulant",
         "benzodiazepine_load"="benzodiazepine",
         "mood_stabilizer_load"="mood_stabilizer",
         "non_benzodiazepine_anxiolytic_sedative_load"="nbas",
         "other_psychotropic_medication_load"="other_psychotropic_medication")

# set NA medications to zero
ember_data_saved$antidepressant_load[which(is.na(ember_data_saved$antidepressant_load))] <- 0
ember_data_saved$antipsychotic_load[which(is.na(ember_data_saved$antipsychotic_load))] <- 0
ember_data_saved$benzodiazepine_load[which(is.na(ember_data_saved$benzodiazepine_load))] <- 0
ember_data_saved$non_benzodiazepine_anxiolytic_sedative_load[which(is.na(ember_data_saved$non_benzodiazepine_anxiolytic_sedative_load))] <- 0
ember_data_saved$mood_stabilizer_load[which(is.na(ember_data_saved$mood_stabilizer_load))] <- 0
ember_data_saved$other_psychotropic_medication_load[which(is.na(ember_data_saved$other_psychotropic_medication_load))] <- 0
ember_data_saved$stimulant_load[which(is.na(ember_data_saved$stimulant_load))] <- 0

# binarize medications: 0 = 0; 1 = > 0
ember_data_saved <- ember_data_saved %>%
  mutate(antidepressant_load = factor(ifelse(antidepressant_load > 0, 1, 0))) %>%
  mutate(antipsychotic_load = factor(ifelse(antipsychotic_load > 0, 1, 0))) %>%
  mutate(benzodiazepine_load = factor(ifelse(benzodiazepine_load > 0, 1, 0))) %>%
  mutate(non_benzodiazepine_anxiolytic_sedative_load = factor(ifelse(non_benzodiazepine_anxiolytic_sedative_load > 0, 1, 0))) %>%
  mutate(mood_stabilizer_load = factor(ifelse(mood_stabilizer_load > 0, 1, 0))) %>%
  mutate(other_psychotropic_medication_load = factor(ifelse(other_psychotropic_medication_load > 0, 1, 0))) %>%
  mutate(stimulant_load = factor(ifelse(stimulant_load > 0, 1, 0))) %>%
  as.data.frame()

# set reference level for medications
ember_data_saved$antidepressant_load <- relevel(ember_data_saved$antidepressant_load, ref = "0")
ember_data_saved$antipsychotic_load <- relevel(ember_data_saved$antipsychotic_load, ref = "0")
ember_data_saved$benzodiazepine_load <- relevel(ember_data_saved$benzodiazepine_load, ref = "0")
ember_data_saved$non_benzodiazepine_anxiolytic_sedative_load <- relevel(ember_data_saved$non_benzodiazepine_anxiolytic_sedative_load, ref = "0")
ember_data_saved$mood_stabilizer_load <- relevel(ember_data_saved$mood_stabilizer_load, ref = "0")
ember_data_saved$stimulant_load <- relevel(ember_data_saved$stimulant_load, ref = "0")
ember_data_saved$other_psychotropic_medication_load <- relevel(ember_data_saved$other_psychotropic_medication_load, ref = "0")

# set reference level for age cagtegory
ember_data_saved$age_bin <- relevel(ember_data_saved$age_bin, ref = 'adult')
```

## Apply I/E Criteria

```{r}
# per protocol only
if(per_protocol_cohort){
  print("Per Protocol Cohort")
  ember_data_saved <- ember_data_saved %>% filter(per_protocol == 1)
}else{
  print("Intention to Treat Cohort")
}

# exclude adolescents
adolecent_ids <- unique(ember_data_saved$client_id[which(ember_data_saved$age_years < 18)])
ember_data_saved <- ember_data_saved[!ember_data_saved$client_id %in% adolecent_ids, ]

ember_data_saved <- ember_data_saved %>%
  filter(age_bin != 'adolescent')
ember_data_saved$age_bin <- droplevels(ember_data_saved$age_bin)

# exclude anyone in pre-treatment or ongoing treatment phase
ember_data_saved <- ember_data_saved %>% filter(foundation_completion_status != "Pre/In Treatment")

# exclude long-term care (LTC) visits
ember_data_saved <- ember_data_saved[ember_data_saved$date_submitted_phq <= ember_data_saved$first_ltc_infusion_date | is.na(ember_data_saved$first_ltc_infusion_date), ]

# exclude outcomes with missing underlying items
missing_items <- which(is.na(ember_data_saved[, grep('phq[1-9]$', names(ember_data_saved), value = T)]), arr.ind = T)
missing_items <- missing_items[, 1]

print(sprintf("Excluding outcomes from %s observations", length(missing_items)))
print(ember_data_saved$client_id[missing_items])

ember_data_saved$phq_tot[missing_items] <- NA
```

## Main effects model

## Fit models with various time terms: linear, quadratic, log-mod

```{r}
# linear
fit_linear <- lmer(phq_tot ~ baseline_phq + age_years_centered_scaled + sex_assigned_at_birth + per_protocol +  
    primary_diagnosis_bipolar + comorbid_anxiety + comorbid_ocd + 
    comorbid_ptsd + comorbid_sud + baseline_si_any + antidepressant_load + 
    antipsychotic_load + benzodiazepine_load + mood_stabilizer_load + 
    non_benzodiazepine_anxiolytic_sedative_load + other_psychotropic_medication_load + 
    stimulant_load + time_first_infusion_to_phq_centered + (1 | 
    client_id), data = ember_data_saved, REML = FALSE)

# quadratic
fit_quadratic <- lmer(phq_tot ~ baseline_phq + age_years_centered_scaled + sex_assigned_at_birth + per_protocol + 
    primary_diagnosis_bipolar + comorbid_anxiety + comorbid_ocd + 
    comorbid_ptsd + comorbid_sud + baseline_si_any + antidepressant_load + 
    antipsychotic_load + benzodiazepine_load + mood_stabilizer_load + 
    non_benzodiazepine_anxiolytic_sedative_load + other_psychotropic_medication_load + 
    stimulant_load + poly(time_first_infusion_to_phq_centered, degree = 2) + (1 | 
    client_id), data = ember_data_saved, REML = FALSE)

# log-mod
fit_log_mod <- lmer(phq_tot ~ baseline_phq + age_years_centered_scaled + sex_assigned_at_birth + per_protocol + 
    primary_diagnosis_bipolar + comorbid_anxiety + comorbid_ocd + 
    comorbid_ptsd + comorbid_sud + baseline_si_any + antidepressant_load + 
    antipsychotic_load + benzodiazepine_load + mood_stabilizer_load + 
    non_benzodiazepine_anxiolytic_sedative_load + other_psychotropic_medication_load + 
    stimulant_load + time_first_infusion_to_phq_log_mod + (1 | 
    client_id), data = ember_data_saved, REML = FALSE)
```

### ANOVAs

```{r}
anova(fit_linear, fit_quadratic)
```

```{r}
anova(fit_linear, fit_log_mod)
```

```{r}
anova(fit_quadratic, fit_log_mod)
```

### R-marginal and R-conditional

```{r}
MuMIn::r.squaredGLMM(fit_linear)
```

```{r}
MuMIn::r.squaredGLMM(fit_quadratic)
```

```{r}
MuMIn::r.squaredGLMM(fit_log_mod)
```

### 

## Interaction model

```{r}
fit_interaction_linear <- 
  lmer(phq_tot ~ baseline_phq + 
         time_first_infusion_to_phq_centered *   (sex_assigned_at_birth + age_years_centered_scaled + per_protocol + 
                                                 primary_diagnosis_bipolar + comorbid_anxiety + 
                                                 comorbid_ocd + comorbid_ptsd + comorbid_sud + 
                                                 baseline_si_any + 
                                                 antidepressant_load + antipsychotic_load + 
                                                 benzodiazepine_load + non_benzodiazepine_anxiolytic_sedative_load + 
                                                 mood_stabilizer_load + 
                                                 stimulant_load + 
                                                 other_psychotropic_medication_load) +
         (1|client_id), 
       data = ember_data_saved, 
       REML = TRUE)


fit_interaction_quadratic <- 
  lmer(phq_tot ~ baseline_phq + 
         poly(time_first_infusion_to_phq_centered, degree=2) *   (sex_assigned_at_birth + age_years_centered_scaled + per_protocol + 
                                                 primary_diagnosis_bipolar + comorbid_anxiety + 
                                                 comorbid_ocd + comorbid_ptsd + comorbid_sud + 
                                                 baseline_si_any + 
                                                 antidepressant_load + antipsychotic_load + 
                                                 benzodiazepine_load + non_benzodiazepine_anxiolytic_sedative_load + 
                                                 mood_stabilizer_load + 
                                                 stimulant_load + 
                                                 other_psychotropic_medication_load) +
         (1|client_id), 
       data = ember_data_saved, 
       REML = TRUE)

fit_interaction_log_mod <- 
  lmer(phq_tot ~ baseline_phq + 
         time_first_infusion_to_phq_log_mod *   (sex_assigned_at_birth + age_years_centered_scaled + per_protocol + 
                                                 primary_diagnosis_bipolar + comorbid_anxiety + 
                                                 comorbid_ocd + comorbid_ptsd + comorbid_sud + 
                                                 baseline_si_any + 
                                                 antidepressant_load + antipsychotic_load + 
                                                 benzodiazepine_load + non_benzodiazepine_anxiolytic_sedative_load + 
                                                 mood_stabilizer_load + 
                                                 stimulant_load + 
                                                 other_psychotropic_medication_load) +
         (1|client_id), 
       data = ember_data_saved, 
       REML = TRUE)
```

### ANOVAs

```{r}
anova(fit_interaction_linear, fit_interaction_quadratic)
```

```{r}
anova(fit_interaction_linear, fit_interaction_log_mod)
```

```{r}
anova(fit_interaction_quadratic, fit_interaction_log_mod)
```

### R-marginal and R-conditional

```{r}
MuMIn::r.squaredGLMM(fit_interaction_linear)
```

```{r}
MuMIn::r.squaredGLMM(fit_interaction_quadratic)
```

```{r}
MuMIn::r.squaredGLMM(fit_interaction_log_mod)
```

## Nested site: Main effects model

```{r}
fit_log_mod_no_site <- lmer(phq_tot ~ baseline_phq + age_years_centered_scaled + sex_assigned_at_birth + per_protocol + 
    primary_diagnosis_bipolar + comorbid_anxiety + comorbid_ocd + 
    comorbid_ptsd + comorbid_sud + baseline_si_any + antidepressant_load + 
    antipsychotic_load + benzodiazepine_load + mood_stabilizer_load + 
    non_benzodiazepine_anxiolytic_sedative_load + other_psychotropic_medication_load + 
    stimulant_load + time_first_infusion_to_phq_log_mod + (1 | 
    client_id), data = ember_data_saved, REML = FALSE)

fit_log_mod_site <- lmer(phq_tot ~ baseline_phq + age_years_centered_scaled + sex_assigned_at_birth + per_protocol + 
    primary_diagnosis_bipolar + comorbid_anxiety + comorbid_ocd + 
    comorbid_ptsd + comorbid_sud + baseline_si_any + antidepressant_load + 
    antipsychotic_load + benzodiazepine_load + mood_stabilizer_load + 
    non_benzodiazepine_anxiolytic_sedative_load + other_psychotropic_medication_load + 
    stimulant_load + time_first_infusion_to_phq_log_mod + (1 | 
    primary_office/client_id), data = ember_data_saved, REML = FALSE)
```

### ANOVA

```{r}
anova(fit_log_mod_no_site, fit_log_mod_site)
```

### R-marginal and R-conditional

```{r}
MuMIn::r.squaredGLMM(fit_log_mod_no_site)
```

```{r}
MuMIn::r.squaredGLMM(fit_log_mod_site)
```

## Nested site: Interaction model

```{r}
fit_interaction_log_mod_no_site <- 
  lmer(phq_tot ~ baseline_phq + 
         time_first_infusion_to_phq_log_mod *   (sex_assigned_at_birth + age_years_centered_scaled + per_protocol + 
                                                 primary_diagnosis_bipolar + comorbid_anxiety + 
                                                 comorbid_ocd + comorbid_ptsd + comorbid_sud + 
                                                 baseline_si_any + 
                                                 antidepressant_load + antipsychotic_load + 
                                                 benzodiazepine_load + non_benzodiazepine_anxiolytic_sedative_load + 
                                                 mood_stabilizer_load + 
                                                 stimulant_load + 
                                                 other_psychotropic_medication_load) +
         (1|client_id), 
       data = ember_data_saved, 
       REML = TRUE)

fit_interaction_log_mod_site <- 
  lmer(phq_tot ~ baseline_phq + 
         time_first_infusion_to_phq_log_mod *   (sex_assigned_at_birth + age_years_centered_scaled + per_protocol + 
                                                 primary_diagnosis_bipolar + comorbid_anxiety + 
                                                 comorbid_ocd + comorbid_ptsd + comorbid_sud + 
                                                 baseline_si_any + 
                                                 antidepressant_load + antipsychotic_load + 
                                                 benzodiazepine_load + non_benzodiazepine_anxiolytic_sedative_load + 
                                                 mood_stabilizer_load + 
                                                 stimulant_load + 
                                                 other_psychotropic_medication_load) +
         (1|primary_office/client_id), 
       data = ember_data_saved, 
       REML = TRUE)
```

### ANOVA

```{r}
anova(fit_interaction_log_mod_no_site, fit_interaction_log_mod_site)
```

### R-marginal and R-conditional

```{r}
MuMIn::r.squaredGLMM(fit_interaction_log_mod_no_site)
```

```{r}
MuMIn::r.squaredGLMM(fit_interaction_log_mod_site)
```
